---
title: "p8105_hw1_gc2942"
output: github_document
---
# Problem 1
The chunk below creates a dataframe containing a random sample of size 10 from a standard Normal distribution, construct a logical vector, takes a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”("Good","Very Good","Excellent").

```{r setup,include = FALSE}
library(tidyverse)
```

```{r}
hw_df = tibble(
  sample = rnorm(10),
  gr_than_0 = sample > 0,
  vec_char = c("I","will","go","to","Mailman","School","of","Public","School", "tommorrow"),
  vec_factor = factor(c("Good","Very Good","Excellent","Good","Very Good","Excellent","Good","Very Good","Excellent","Good"))
)
 mean(pull(hw_df, sample))
 mean(pull(hw_df, gr_than_0)) 
```

I can take the mean of sample from standard normal distribution and a logical vector, but I fail to run the mean for a character vector and a factor vector.Therefore, I write the following code and try to convert those variables from one type to numeric.

```{r, eval=FALSE}
  as.numeric((pull(hw_df, gr_than_0)) 
  as.numeric(pull(hw_df,vec_char))
  as.numeric(pull(hw_df,vec_factor))
```

The result shows that it is impossible to convert a character vector into a  numerical number. However, we can assign the number to an ordinal variable.

## Problem 2


```{r}
data("penguins", package = "palmerpenguins")

```
We first download the penguins data set. 
There are `r nrow(penguins)` and `r ncol(penguins)` within the data set. 
Variables are included `r names(penguins)`.
The mean flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE)`.

Then we make the scatterplot for penguins.
```{r,warning=FALSE}
ggplot(penguins,aes(x = bill_length_mm, 
        y = flipper_length_mm,
        color =  species)) + geom_point() 
ggsave("scatter_plot.pdf", height = 4, width = 6)
```






